Har en persons høyde innvirkning på lønnen?

### 2020-10-09 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
Regresjonsanalyser til test

```{r boxplot-høyde-inntekt, echo=FALSE}
heightsPosInc <- subset(heights, inntekt < 1000000)
ggplot(heightsPosInc, mapping = aes(x = height_cmInt, y = inntekt)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot()
```

@@

>>>>

```{r boxplot-høyde-inntekt, echo=FALSE}
heightsPosInc <- subset(heights, inntekt < 1000000)
ggplot() +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot(heights, 
               mapping = aes(
                 x = height_cmInt, 
                 y = inntekt), 
               ymin = 50000, 
               ymax = 700000,
               colour = "darkgreen")
```

@@

### Regresjon

```{r}
summary(lm(inntekt ~ height_cm, data = heights))
```

```{r}
summary(lm(inntekt ~ education + height_cm + sex + weight + afqt + marital, data = heights))
```
